\subsubsection{Example: INT50-CPP}

\begin{frame}[t]{Enumerations and integers (INT50-CPP)}
\begin{itemize}
  \item Enumerations in C++.
    \begin{itemize}
      \item Unscoped enumerations $\rightarrow$ underlying type is not fixed.
      \item Scoped enumerations $\rightarrow$ underlying type is fixed.
    \end{itemize}

  \vfill
  \item An enumeration object may represent any value of the underlying type.
    \begin{itemize}
      \item Even if it is not a valid enumerator.
    \end{itemize}

  \vfill
  \item When converting arithmetic value to enumeration, ensure it is a valid enumerator.
    \begin{itemize}
      \item Perform checks before conversion (i.e. \emph{cast}).
      \item An integer may be not representable by the underlying type.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Bounds checking}
\begin{columns}

\column{.5\textwidth}
\begin{block}{Original}
\begin{lstlisting}
enum level { low, medium, high };

void print(int n) {
  level l = static_cast<level>(n);
  if (l<low || l>high) throw level_error;
  //...
}
\end{lstlisting}
\end{block}

\pause
\column{.5\textwidth}
\begin{block}{Compliant}
\begin{lstlisting}[escapechar=@]
enum level { low, medium, high };

void print(int n) {
  @{\bf\color{red}if (n<low || n>high) throw level\_error}@;
  level l = static_cast<level>(n);
  //...
}
\end{lstlisting}
\end{block}

\end{columns}
\end{frame}

\begin{frame}[t,fragile]{Even better}
\begin{columns}

\column{.5\textwidth}
\begin{block}{Compliant}
\begin{lstlisting}[escapechar=@]
enum @\textbad{class}@ level { low, medium, high };

void print(int n) {
  level l = static_cast<level>(n);
  @{\bf\color{red}if (l<level::low || l>level::high) throw level\_error}@;
  //...
}
\end{lstlisting}
\end{block}

\pause
\column{.5\textwidth}
\begin{block}{Compliant}
\begin{lstlisting}[escapechar=@]
enum level @\textbad{: int}@ { 
  low, medium, high 
};

void print(int n) {
  level l = static_cast<level>(n);
  @{\bf\color{red}if (l<level::low || l>level::high) throw level\_error;}@
  //...
}
\end{lstlisting}
\end{block}

\end{columns}
\end{frame}

\begin{frame}[t]{Risk assesment}
\begin{itemize}
  \item Unspecified values may result in buffer overflows and arbitrary code execution.
    \begin{itemize}
      \item Severity $\rightarrow$ Medium.
    \end{itemize}

  \vfill
  \item Enumerations are rarely used for indexing into arrays.
    \begin{itemize}
      \item Likelihood $\rightarrow$ Unlikely.
    \end{itemize}

  \vfill
  \item May be detected by tool but need manual correction.
    \begin{itemize}
      \item Remediation cost $\rightarrow$ Medium.
    \end{itemize}

  \vfill
  \item Priority 4 $\Rightarrow$ Level 3.
\end{itemize}
\end{frame}
