\subsubsection{Example: MEM56-CPP}

\begin{frame}[t]{Owned pointers and smart pointers (MEM56-CPP)}
\begin{itemize}
  \item Smart pointers (e.g.: \cppid{std::unique\_ptr}, \cppid{std::shared\_ptr})
        include ownership as part of resource management.
    \begin{itemize}
      \item If you pass a pointer to the constructor, memory is now \textmark{owned}
            by the created smart pointer.
    \end{itemize}

  \vfill
  \item Getting back the ownership of a \cppid{std::unique\_ptr}:
    \begin{itemize}
      \item \cppid{p.release()}.
    \end{itemize}

  \vfill 
  \item Getting the pointer but the \cppid{std::unique\_ptr} stills own it:
    \begin{itemize}
      \item \cppid{p.get()}.
    \end{itemize}

  \vfill
  \item The pointerin a \cppid{std::shared\_ptr} is changed but the old one is released:
    \begin{itemize}
      \item \cppid{p.reset(ptr)}.
    \end{itemize}    
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Using \cppid{shared\_ptr}}
\begin{columns}

\column{.5\textwidth}
\begin{block}{Original}
\begin{lstlisting}
#include <memory>

void f() {
  int * p = new int;
  std::shared_ptr<int> q1{p};
  std::shared_ptr<int> q2{p};
  //...
}
\end{lstlisting}
\end{block}

\pause
\column{.5\textwidth}
\begin{block}{Compliant}
\begin{lstlisting}[escapechar=@]
#include <memory>

void f() {
  int * p = new int;
  auto q1 = make_shared<int>();
  auto q2 = q1;
  //...
}
\end{lstlisting}
\end{block}

\end{columns}
\end{frame}

\begin{frame}[t,fragile]{More subtle example}
\begin{block}{Original}
\begin{lstlisting}
#include <memory>

struct B {
  virtual ~B() = default;
};

struct D : B {};

void g(std::shared_ptr<D> pder);

void f() {
  std::shared_ptr<B> poly{new D};
  g(std::shared_ptr<D>{dynamic_cast<D*>(poly.get())});
}
\end{lstlisting}
\end{block}
\vfill
\begin{itemize}
  \item Passing to \cppid{g()} a \cppid{shared\_ptr<D>} built from the
        internal pointer of \cppid{poly}.
\end{itemize}
\end{frame}

\begin{frame}[t,fragile]{Using dynamic\_pointer\_cast<>}
\begin{block}{Compliant}
\begin{lstlisting}[escapechar=@]
#include <memory>

struct B {
  virtual ~B() = default;
};

struct D : B {};

void g(std::shared_ptr<D> pder);

void f() {
  std::shared_ptr<B> poly{new D};
  g(@{\bf\color{red}dynamic\_pointer\_cast}@<D,B>(poly));
}
\end{lstlisting}
\end{block}
\vfill
\end{frame}

\begin{frame}[t]{Risk assesment}
\begin{itemize}
  \item It may lead to double free or to a deallocation by a not matching allocation.
    \begin{itemize}
      \item Severity $\rightarrow$ High.
    \end{itemize}

  \vfill
  \item It is difficult to find.
    \begin{itemize}
      \item Likelihood $\rightarrow$ Likely.
    \end{itemize}

  \vfill
  \item May be detected by tool but need manual correction.
    \begin{itemize}
      \item Remediation cost $\rightarrow$ Medium.
    \end{itemize}

  \vfill
  \item Priority 18 $\Rightarrow$ Level 1.
\end{itemize}
\end{frame}
