\section{Coding standards}

\begin{frame}[t]{Available coding standards}
\begin{itemize}
  \item Many available coding standards out there.

  \vfill
  \item Organized as sets of rules.

  \vfill
  \item Different goals and priorities.

  \vfill
  \item None of them will perfectly match your organization/project.

  \vfill
  \item Need to customize to specific situation.
\end{itemize}
\end{frame}

\begin{frame}[t]{Why do we want a coding standard?}
\begin{itemize}
  \item Reliability.
  \item Portability.
  \item Maintainability.
  \item Testability.
  \item Reusability.
  \item Readability.
\end{itemize}
\end{frame}

\begin{frame}[t]{Questions on rules}
\begin{itemize}
  \item A rule without a rationale is not useful.
    \begin{itemize}
      \item What are you trying to avoid?
    \end{itemize}

  \vfill\pause
  \item Every rule should include examples:
    \begin{itemize}
      \item Including compliant and non-compliant code as well as compliant solutions.
    \end{itemize}

  \vfill\pause
  \item Every rule should include a risk assesment.

  \vfill\pause
  \item Rules should be enforceable.
    \begin{itemize}
      \item Ideally trhoug rule support.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Some available coding standards}
\begin{itemize}
  \item \textgood{C}:
    \begin{itemize}
      \item CERT C Secure Coding.
      \item MISRA C.
    \end{itemize}

  \item \textgood{C++}:
    \begin{itemize}
      \item Cpp Core Guidelines. Live.
      \item CERT C++ Secure Coding. 2017
      \item High Integrity C++. 2013.
      \item MISRA C++. 2008.
      \item JSF AV C++ Coding Standards. 2005.
    \end{itemize}
\end{itemize}
\end{frame}

\input{jsf-cpp}
\input{cpp-corecpp}
\input{cert-cpp}
