\subsection{C++ Core Guidelines}

\begin{frame}[t]{Goal and contents}
\begin{itemize}
  \item Try to help people to use \textmark{modern C++} effectively.

  \vfill
  \item Addresses multiple concerns.

  \vfill
  \item It is an open initiative.
    \begin{itemize}
      \item Anybody can contribute.
      \item Main editors are Bjarne Stroustrup and Herb Sutter.
      \item Distributed through MIT license.
      \item Available at \textgood{github}.
    \end{itemize}

  \vfill
  \item Source:
    \begin{itemize}
      \item Repo: \textgood{\url{https://github.com/isocpp/CppCoreGuidelines}}.
      \item Web: \textgood{\url{http://isocpp.github.io/CppCoreGuidelines/CppCoreGuidelines}}.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t]{Rules}
\begin{itemize}
  \item C++ Core Guidelines are in continuous development.
    \begin{itemize}
      \item Latest version is 0.8.
    \end{itemize}

  \vfill
  \item A great amount of rules.

  \vfill
  \item Existing support tools for some rules.

  \vfill
  \item Existing support library.
    \begin{itemize}
      \item \textgood{GSL}: Guidelines Support Library.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}[t,shrink]{Rules (900)}
\begin{itemize}
  \item Philosophy: 13.
  \item Interfaces: 30.
  \item Functions: 55.
  \item Classes and class hierarchies: 183.
  \item Enumerations: 8.
  \item Resource management: 37.
  \item Expressions/Statements: 107.
  \item Performance: 30.
  \item Concurrency and Parallelism: 201.
  \item Error handling: 31.
  \item Constants: 5.
  \item Templates: 150.
  \item C-style: 3.
  \item Source files: 22.
  \item Standard library: 25
\end{itemize}
\end{frame}
